An agent-based model for city networks based on interactions between firms

### 2019-09-25 slides.tex
Update on Overleaf.

Cities as maximisation of socio-economic interactions

Network economies \cite{sassen1991global} \cite{castells1996information}

World city network driven by interactions between firms (Taylor, 2001; Martinus and Sigler, 2018)

Asymmetrical spatial interactions -- different relative position of cities

@@

Evolutionary Theory of Urban Systems \cite{pumain1997pour} \cite{pumain2006villes}

Adaptive cycles and diffusion on innovation (H{\"a}gerstrand, 1973)

Path dependence

Selection

Emergent structures

% discussion theorie Denise

@@

Metropolisation vs. regionalisation effects

Relationship local/global of multinational firm linkages (internationalisation)

Specialisation-driven factors for an economic network to emerge

Drivers of innovation

Macroeconomic exogenous chocs and resilience of urban systems

Can we access geographical and economic processes within urban networks of firms with a generative model?

@@

% research question / objective
% du coup je te laisse formuler le broad research question, car je vois pas bien

@@

@@

% comparing with real data?

>>>>

General framework:

\begin{itemize}
    \item Cities as maximisation of socio-economic interactions 
    \item Network economies \cite{sassen1991global} \cite{castells1996information}
    \item World city network driven by interactions between firms (Taylor, 2001; Martinus and Sigler, 2018)
    \item Asymmetrical spatial interactions -- different relative position of cities
\end{itemize}

@@

\begin{itemize}
    \item Evolutionary Theory of Urban Systems \cite{pumain1997pour} \cite{pumain2006villes}
    \item Adaptive cycles and diffusion on innovation (H{\"a}gerstrand, 1973) 
    \item Path dependence \cite{martinsunley2006information}
    \item Selection and emerging structures of systems
\end{itemize}

\bigskip
% discussion theorie Denise
}

@@

Assumptions

\begin{itemize}
    \item Metropolisation vs. regionalisation effects
    \item Relationship local/global of multinational firm linkages 
    \item Specialisation-driven factors and drivers of innovation
    \item Macroeconomic exogenous chocs and resilience of urban systems 
\end{itemize}

How can we approach geographical and economic processes within urban networks of firms with a generative model?

@@

Towards a generative model of urban firm networks

% research question / objective
%

@@

% ok desolee je n'avais pas bien compris

@@

% further comparing with real data?
